\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{titlesec}

\geometry{a4paper, margin=2.5cm}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Frontend Systems - Portfolio Assignment 01}
\fancyhead[R]{\thepage}
\fancyfoot[C]{THWS - Prof. Dr. Peter Braun}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\title{\textbf{Requirements Document\\[0.5em]\Large Rollenreich}}
\author{Frontend Systems - Portfolio Assignment 01}
\date{April 9, 2025}

\begin{document}

\maketitle

\section*{Author Information}
\begin{tabularx}{\textwidth}{l X r}
\textbf{Name} & \textbf{Email} & \textbf{Matrikelnummer} \\
\hline
Maximilian Keller & \href{mailto:maximilian.keller@study.thws.de}{maximilian.keller@study.thws.de} & 5123018 \\
Tom Knoblach & \href{mailto:tom.knoblach@study.thws.de}{tom.knoblach@study.thws.de} & 5123034 \\
David Heppenheimer & \href{mailto:david.heppenheimer@study.thws.de}{david.heppenheimer@study.thws.de} & 5123026 \\
Zacharias Priller & \href{mailto:zacharias.priller@study.thws.de}{zacharias.priller@study.thws.de} & 5123014 \\
\end{tabularx}

\tableofcontents

\newpage

\section{Project Overview}
Rollenreich is a modern e-commerce web application built with React, showcasing a playful concept around luxury and design-focused toilet paper products. It aims to combine humor and high-end shopping experiences, providing users with an intuitive and visually appealing interface to browse and purchase designer toilet paper.

\subsection{Project Background}
The concept was born from the idea that even mundane products like toilet paper can be elevated into lifestyle statements. Rollenreich embraces this by offering extravagant and unique product designs, and serves as a demonstration of technical skills in frontend systems, particularly focusing on component-based design, responsive interfaces, and integration with backend APIs.

\subsection{Target Audience}
The application targets users who:
\begin{itemize}
    \item Appreciate design and novelty in everyday items
    \item Seek unique gifts or collector’s items
    \item Have a higher disposable income and appreciate premium quality
    \item Are interested in eco-conscious, humorous, or limited-edition alternatives
    \item Are tech-savvy and open to online shopping experiences
\end{itemize}

\subsection{Project Goals}
The main goals of the Rollenreich project are:
\begin{itemize}
    \item Deliver a functional and visually consistent React application with a modular component structure
    \item Implement smooth navigation between multiple views using React Router
    \item Enable interaction with a backend API through asynchronous calls (e.g., product loading, order submission)
    \item Provide a responsive, usable layout for both desktop and mobile users
    \item Ensure every feature is accessible through the UI (no manual URL manipulation required)
    \item Meet accessibility and performance guidelines
\end{itemize}

\section{Key Features}
Features are divided into must-have and nice-to-have based on importance for MVP delivery and alignment with course requirements.

\subsection{Must-have Features}
\begin{enumerate}[label=\textbf{MF\arabic*:}]
    \item \textbf{Product Catalog} - Clear presentation of all products with filter functions by categories (Luxury, Brand Collaborations, Eco-Friendly), prices, and availability.
    \item \textbf{User Accounts} - Registration and login system with personal profile, order history, and saved payment information.
    \item \textbf{Shopping Cart and Checkout} - Functional shopping cart with quantity adjustment and a multi-step checkout process.
    \item \textbf{Product Detail Pages} - Detailed information on each product with high-quality images, descriptions, prices, and availability.
    \item \textbf{Responsive Design} - Full functionality on all devices (Desktop, Tablet, Smartphone).
    \item \textbf{Search Functionality} - Search function for products with filters and sorting options.
    
    % TODO: Subscription model is subject to change and switch places depending on Peter's feedback
\end{enumerate}
% alternative:
%\subsection{Must-have Features}
%\begin{enumerate}[label=\textbf{MF\arabic*:}]
%    \item \textbf{Product Catalog with Filters} – Component for browsing and filtering products by category, price, availability.
%    \item \textbf{Responsive Layout} – Responsive views that adjust to desktop, tablet, and mobile devices.
%    \item \textbf{User Accounts} – Register, log in, and manage user profile (with persistent state across sessions).
%    \item \textbf{Shopping Cart \& Checkout Flow} – Add/remove items, quantity adjustment, and guest/registered checkout views.
%    \item \textbf{Product Detail View} – Dedicated view with high-resolution images, descriptions, and availability info.
%    \item \textbf{API Integration} – Fetch product data and post orders via asynchronous backend calls (fetch/axios).
%    \item \textbf{Navigation Between Views} – Implemented via React Router with routes like `/home`, `/products/:id`, `/checkout`, etc.
%\end{enumerate}

\subsection{Nice-to-have Features}
\begin{enumerate}[label=\textbf{NF\arabic*:}]
    % TODO: Subscription model is subject to change and switch places depending on Peter's feedback
    \item \textbf{Subscription Models} - Regular delivery of toilet paper with discount benefits and exclusive products.
    
    \item \textbf{Payment Options} - Support for various payment methods (credit card, PayPal, direct debit).´
    \item \textbf{Review System} - Ability for customers to rate products and leave reviews.
    \item \textbf{Newsletter System} - Sign-up for regular updates on new products and special offers.
    \item \textbf{Wishlist} - Ability to save products for later purchase.
    \item \textbf{Social Media Integration} - Sharing products on various social platforms.
    \item \textbf{Limited Editions} - Time-limited special offers and exclusive collections.
\end{enumerate}
% alternative:
%\subsection{Nice-to-have Features}
%\begin{enumerate}[label=\textbf{NF\arabic*:}]
%    \item \textbf{Subscription Models} – Selectable delivery plans (e.g., monthly) with recurring payment support.
%    \item \textbf{Review System} – Allow users to rate and review purchased items.
%    \item \textbf{Newsletter Integration} – Sign-up and unsubscribe system with double opt-in.
%    \item \textbf{Wishlist Feature} – Save favorite products across sessions.
%    \item \textbf{Limited Editions} – Special categories or badges for time-limited items.
%    \item \textbf{Social Media Sharing} – Basic share buttons on product pages.
%\end{enumerate}

\section{User Roles and Interactions}
Rollenreich serves different types of users with varying needs and interaction patterns.

\subsection{User Role 1: Unregistered Visitor}
\begin{itemize}
    \item \textbf{Description:} First-time or occasional visitors to the website who have not yet created a user account.
    \item \textbf{Responsibilities:} No specific responsibilities within the system.
    \item \textbf{Key Interactions:}
    \begin{itemize}
        \item Browsing the product catalog
        \item Reading product reviews
        \item Adding products to the shopping cart
        \item Performing a guest checkout
        \item Registering for a user account
        \item Signing up for the newsletter
    \end{itemize}
\end{itemize}

\subsection{User Role 2: Registered Customer}
\begin{itemize}
    \item \textbf{Description:} Users with an account who shop regularly or want to use the benefits of being a registered user.
    \item \textbf{Responsibilities:} Maintaining their own account information, adhering to terms of service.
    \item \textbf{Key Interactions:}
    \begin{itemize}
        \item Logging in and managing personal profile
        \item Saving delivery and payment information
        \item Viewing order history
        \item Writing product reviews
        \item Managing subscriptions (if applicable)
        \item Creating and editing wishlists
        \item Participating in loyalty programs
    \end{itemize}
\end{itemize}

\subsection{User Role 3: Subscriber}
\begin{itemize}
    \item \textbf{Description:} Registered customers who have signed up for a regular delivery subscription for toilet paper.
    \item \textbf{Responsibilities:} Ensuring up-to-date payment information, timely modification or cancellation of subscriptions.
    \item \textbf{Key Interactions:}
    \begin{itemize}
        \item Selecting and customizing subscription plans
        \item Changing delivery frequency
        \item Pausing or canceling subscriptions
        \item Accessing exclusive subscriber offers
        \item Managing automatic payments
    \end{itemize}
\end{itemize}

\subsection{User Role 4: Administrator}
\begin{itemize}
    \item \textbf{Description:} Staff members with comprehensive rights to manage the webshop.
    \item \textbf{Responsibilities:} Maintaining the product catalog, processing orders, customer management.
    \item \textbf{Key Interactions:}
    \begin{itemize}
        \item Adding, editing, and removing products
        \item Managing orders and order statuses
        \item Handling customer data and inquiries
        \item Moderating product reviews
        \item Creating and sending newsletters
        \item Monitoring system status
        \item Generating reports and statistics
    \end{itemize}
\end{itemize}

\section{User Stories / Use Cases}
The following describe the main user stories and use cases for the Rollenreich webshop.

\subsection{User Story 1: Product Search and Purchase}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{ID} & US-001 \\
\hline
\textbf{Title} & Search for and Purchase a Luxury Toilet Paper Roll \\
\hline
\textbf{User Role} & Unregistered Visitor \\
\hline
\textbf{Description} & As an \textit{unregistered visitor}, I want to \textit{search for luxury toilet paper rolls and purchase one}, so that \textit{I can find a special gift for a friend}. \\
\hline
\textbf{Acceptance Criteria} &
\begin{itemize}[noitemsep, topsep=0pt]
    \item User can use the search function to search for "Luxury" or "Gold".
    \item User can filter products by price, availability, and category.
    \item User can view product details and reviews.
    \item User can add a product to the shopping cart.
    \item User can complete the checkout process as a guest.
    \item User receives an order confirmation via email.
\end{itemize} \\
\hline
\textbf{Priority} & High \\
\hline
\end{tabularx}

\subsection{User Story 2: Create User Account}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{ID} & US-002 \\
\hline
\textbf{Title} & Create a User Account \\
\hline
\textbf{User Role} & Unregistered Visitor \\
\hline
\textbf{Description} & As an \textit{unregistered visitor}, I want to \textit{create a user account}, so that \textit{I can track my orders and benefit from regular customer advantages}. \\
\hline
\textbf{Acceptance Criteria} &
\begin{itemize}[noitemsep, topsep=0pt]
    \item User can create an account via a "Register" button.
    \item User must provide email, password, and personal information.
    \item System validates the email address format and password strength.
    \item User receives a confirmation email (possibly with an activation link).
    \item After activation/confirmation, the user can log in with their credentials.
    \item User can view and edit their profile after logging in.
\end{itemize} \\
\hline
\textbf{Priority} & High \\
\hline
\end{tabularx}

\subsection{User Story 3: Set Up Subscription}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{ID} & US-003 \\
\hline
\textbf{Title} & Set Up a Toilet Paper Subscription \\
\hline
\textbf{User Role} & Registered Customer \\
\hline
\textbf{Description} & As a \textit{registered customer}, I want to \textit{set up a regular delivery subscription for toilet paper}, so that \textit{I never run out and can benefit from discounts}. \\
\hline
\textbf{Acceptance Criteria} &
\begin{itemize}[noitemsep, topsep=0pt]
    \item User can choose from various subscription options (e.g., monthly, quarterly).
    \item User can specify the product type and quantity for the subscription.
    \item System clearly displays discounts and benefits of the subscription.
    \item User must provide payment information for recurring payments.
    \item User receives confirmation of the established subscription.
    \item User can view and manage the subscription in their profile at any time.
\end{itemize} \\
\hline
\textbf{Priority} & Medium \\
\hline
\end{tabularx}

\subsection{User Story 4: Submit Product Review}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{ID} & US-004 \\
\hline
\textbf{Title} & Submit a Product Review \\
\hline
\textbf{User Role} & Registered Customer \\
\hline
\textbf{Description} & As a \textit{registered customer}, I want to \textit{submit a review for a recently purchased product}, so that \textit{I can share my experience with other customers and provide feedback to the manufacturer}. \\
\hline
\textbf{Acceptance Criteria} &
\begin{itemize}[noitemsep, topsep=0pt]
    \item User can only review products they have actually purchased.
    \item Review system allows star rating (1-5) and text comments.
    \item User can optionally upload photos with their review.
    \item Reviews are moderated before being published.
    \item Other users can mark reviews as helpful.
    \item User can edit or delete their own reviews later.
\end{itemize} \\
\hline
\textbf{Priority} & Medium \\
\hline
\end{tabularx}

\subsection{User Story 5: Newsletter Sign-up}
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{ID} & US-005 \\
\hline
\textbf{Title} & Sign Up for Newsletter \\
\hline
\textbf{User Role} & Unregistered Visitor / Registered Customer \\
\hline
\textbf{Description} & As a \textit{visitor or registered customer}, I want to \textit{sign up for the newsletter}, so that \textit{I can be informed about new products, offers, and promotions}. \\
\hline
\textbf{Acceptance Criteria} &
\begin{itemize}[noitemsep, topsep=0pt]
    \item User can find a newsletter sign-up form (e.g., in the footer or a dedicated section).
    \item User needs to provide a valid email address.
    \item System validates the email address format.
    \item User receives a confirmation message upon successful sign-up (potentially requires double opt-in via email confirmation).
    \item User can easily unsubscribe from the newsletter (e.g., via a link in the email).
    \item Administrator can manage the list of subscribers.
\end{itemize} \\
\hline
\textbf{Priority} & Low \\
\hline
\end{tabularx}

\section{Non-Functional Requirements}
Beyond the specific features, the application must meet the following quality attributes:

\subsection{Usability}
The webshop must be intuitive and easy to navigate. Key information (products, prices, cart) should be easily accessible. The checkout process must be clear and straightforward. Consistency in design and interaction patterns across the application is required.

\subsection{Responsiveness}
The application must be fully responsive and provide an optimal viewing and interaction experience across a wide range of devices, including desktops, tablets, and smartphones. Layouts should adapt gracefully to different screen sizes and orientations.

\subsection{Accessibility}
The webshop should strive to meet WCAG 2.1 Level AA guidelines. This includes providing text alternatives for non-text content, ensuring keyboard navigability, sufficient color contrast, and compatibility with common assistive technologies.

\subsection{Performance}
Interactions (e.g., adding to cart, filtering products, navigating pages) should feel instantaneous. Backend response times and queries should be optimized, and frontend assets (images, scripts) should be efficiently managed.

\subsection{Security}
User data (personal information, payment details) must be handled securely. Input validation must be implemented on both frontend and backend. Secure practices for authentication, session management, and data transmission are mandatory.
% alternative:
%\section{Non-Functional Requirements}

%\subsection{Usability}
%Design will be intuitive and follow common UI conventions. All actions (like checkout, subscription management) will be accessible through clear UI elements.

%\subsection{Responsiveness}
%The app will use CSS media queries and responsive components to ensure a good experience across mobile and desktop screen sizes.

%\subsection{Accessibility}
%UI will consider WCAG 2.1 Level AA standards. Semantic HTML, focus indicators, ARIA labels, and sufficient contrast will be implemented.

%\subsection{Performance}
%React code will be optimized via lazy loading and effective state management. Static assets will be optimized for web delivery.

%\subsection{Security}
%Secure API usage, HTTPS enforcement, input validation, and no exposure of sensitive user data. Authentication will follow best practices.


\section{Technology Assumptions}
\begin{itemize}
    \item \textbf{Frontend Framework:} The application will be developed using the Next.js framework, which combines both frontend and backend in a React-based environment.
    \item \textbf{Styling:} Tailwind CSS will be used for styling the application, enabling utility-first design and consistent styling across components through a scalable and maintainable approach.
    \item \textbf{Backend Interaction:} The frontend will communicate with backend routes using standard Next.js API endpoints, leveraging built-in functionality for server-side logic.
    \item \textbf{Backend Technology:} Backend logic will be integrated into the Next.js application using its built-in API routes.
    \item \textbf{Database \& ORM:} PostgreSQL will be used as the database system, with Prisma as the Object-Relational Mapper (ORM) to enable type-safe and efficient database access.
    \item \textbf{Version Control:} Git will be used for version control, with the repository hosted on GitHub.
    \item \textbf{Containerization:} The entire application stack, including the Next.js app and PostgreSQL database, will be containerized and orchestrated using Docker Compose for simplified local development and deployment.
\end{itemize}

\section{Project Constraints}
\begin{itemize}
    \item \textbf{Timeline:} The project must be completed within the timeframe specified by the Frontend Systems course, including the final submission deadline (2025-07-30).
    \item \textbf{Team Size:} The development team consists of 4 students. Workload distribution and collaboration are key constraints.
    \item \textbf{Scope Limitation:} Due to time constraints, not all "Nice-to-have" features may be fully implemented. Priority will be given to "Must-have" features and core functionality.
    \item \textbf{Resource Availability:} The project relies on the availability and stability of the custom-built backend API. Any changes in the backend may affect the frontend development.
    \item \textbf{Technology Stack:} The mandatory use of React for the frontend dictates certain architectural choices and development practices.
\end{itemize}

\section*{Acknowledgement of AI Technologies}
This document was firstly drafted and refined collaboratively using Gemini 2.5 Pro based on an outline containing related information. The authors reviewed, revised, and enhanced the Gemini 2.5 Pro
output with additional content. 
\end{document}
